---
title: "Project 2--Modeling"
author: "YOUR NAME HERE"
date: '`r format(Sys.time(), "%A, %B %d, %Y @ %I:%M %p")`'
output: 
  html_document: 
    theme: yeti
    highlight: textmate
    code_folding: hide
---

```{r globalopts, include = FALSE}
library(knitr)


opts_chunk$set(comment = "", message = FALSE, warning = FALSE)
```

## {.tabset}

### **Packages/Data**

Load all packages and datasets here. Use `glimpse` to visualize the structure of each dataset.

Packages Used

```{r}
library(dplyr)
library(moderndive)
library(ggplot2)
library(tibble)
```

Fast Food Data

```{r fastfooddata}
fastfooddata <- read.csv(file = url("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/fastfood2017.csv"))
glimpse(fastfooddata)
```

Cookout Burgers Data

```{r cookoutdata}
cookoutdata <- read.csv(file = url("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cookoutburgers.csv"))
glimpse(cookoutdata)
```

Spruce Experiment Data

```{r sprucedata}
sprucedata <- read.csv(file = url("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Chihara/Spruce.csv"))
glimpse(sprucedata)
```

Monopoly Game Data

```{r monopolydata}
monopolydata <- read.csv(file = url("https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/monopolygame.csv"))
glimpse(monopolydata)
```


### **Problem 1**

Nutritionists recommend against eating fast food because it is high in sodium, saturated fat, trans fat, and cholesterol. Eating too much over a long period of time can lead to health problems such as high blood pressure, heart disease, and obesity. Many fast-food meals contain more than an entire day's worth of recommended calories! Read the description for the [`fastfood2017`](https://stat-jet-asu.github.io/Datasets/InstructorDescriptions/fastfood2017.html) dataset and the `cookoutburgers` dataset (on the same page), then use the data to perform the following analysis.

A) For fast-food burgers, create a correlation matrix for all of the nutritional variables except `servingsize`. Round the entries to two decimal places. Overall, how would you describe the relationships between nutritional components in fast-food burgers  (mostly weak, moderate, strong, varied)? Explain.

```{r burgercorr}
fastfooddata <- read.csv(file = "https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/fastfood2017.csv")
fastfoodnumbers <- fastfooddata %>%
  select(calories,totalfat,saturatedfat,transfat,sodium,carbs,sugars,protein)
fastfoodnumbers
#can also be written "select(fastfooddata, A, B, C...)" if you don't want to use %/%
burgercorr <- cor(fastfoodnumbers, use = "pairwise.complete.obs", method = "pearson")
x = round(burgercorr,2)
x
```

**ANSWER:**

B) Create a scatterplot with a fitted line to show the relationship between calories (x) and total fat (y) for fast-food burgers. Add an informative title and better axis labels than the default variable names, including units of measure.

```{r burgerplot}
#attach(fastfoodnumbers)
#plot(calories, totalfat, main = "Scatterplot Example", xlab = "Calories", ylab = "Total Fat")
#abline(lm(total fat, calories), col = "red") 
#regression line(y~x)
#lines(lowess(calories, total fat), col = "red") <~ better fitted line
x = ggplot(fastfooddata, aes(x = calories, y = totalfat)) + labs(title = "Calories to total fat relationship", x = "Calories(what you don't want)", y = "Total Fat(What you really don't want)") + geom_point() + geom_smooth(method = lm, se = FALSE)
x + theme_classic()
```

C) Fit a linear model to explore the relationship between calories (x) and total fat (y) for fast-food burgers. Display your model results using `get_regression_table()` and `get_regression_summaries()` with Markdown-formatted output. 

```{r burgermodel}
burgermodel <- lm(calories~totalfat, fastfooddata)
get_regression_table(burgermodel, digits = 2, print = TRUE)
get_regression_summaries(burgermodel, digits = 2, print = TRUE)
```

D) Use your model and `get_regression_points()` to predict the total fat in the four Cookout burgers. Display the results with Markdown-formatted output. Compare these predictions to the actual total fat values in the `cookoutburgers` dataset. Did your model do a good job of predicting? Explain.

```{r burgerpred}
cookoutdata <- read.csv(file = "https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Instructor/cookoutburgers.csv")
cookoutnumbers <- cookoutdata %>%
  select(calories)

cookoutcal <- data.frame(cookoutnumbers)

#burgermodel %>%
  #select(calories)


newpred <- get_regression_points(newburgermodel, newdata = cookoutcal)
newpred



```

**ANSWER:**

E) Suppose someone says, "We can interpret R^2^ as the percentage of calories in each burger that comes from fat." Explain why this is incorrect and give a better interpretation of the R^2^ value for this model in context. 

**ANSWER:**


### **Problem 2**

Case Study 1.10 in the MSRR textbook (p. 10) describes an experiment involving manipulations intended to impact the growth of black spruce seedlings. Load the data in [spruce.csv](https://raw.githubusercontent.com/STAT-JET-ASU/Datasets/master/Chihara/Spruce.csv) and perform the following analysis.

A) Once of the independent variables in the experiment was whether or not seedlings received fertilizer. Create a scatterplot with fitted lines to show the relationship between the heights of seedlings at the start of the experiment (x) and their heights after five years (y), with a separate line for the fertilized and not fertilized groups. Add an informative title and better axis labels than the default variable names, including units of measure.

```{r spruceplot}

```

B) Fit a parallel slopes model to show the height of seedlings after five years as a function of starting height and fertilizer category. Display the `summary()` of your linear model. Interpret the values of the coefficients in context, including units.

```{r sprucemodel}

```

**ANSWER:**

C) Use `get_regression_points()` to extract the fitted values and residuals from the model. Based on this information and other summary measures, do you think this model would do a good job of predicting the heights of other spruce seedlings grown under the same conditions? Explain.

```{r sprucepts}

```

**ANSWER:**


### **Problem 3**

First known as *The Landlord's Game* by its original developers, the game we now know as *Monopoly* was commercially released by Parker Brothers in 1935. There are now over 1000 variations of this classic game in the US and abroad. Read the description for the [`monopoly`](https://stat-jet-asu.github.io/Datasets/InstructorDescriptions/monopoly.html) dataset and use the data to perform the following analysis.

A) Create a scatterplot with fitted lines to show the relationship between the number of spaces from Go (x) and the purchase price of the property (y), with a separate line for each property type. Add an informative title and better axis labels than the default variable names, including units of measure. Would a parallel slopes model be appropriate here? Why or why not? (Note: It is possible to fit parallel slopes models with more than two categories by adding extra terms to the model, so the number of categories is not an issue.)

```{r pricesplot}

```

**ANSWER:**

B) Fit a linear model that predicts property price as a function of spaces from Go for all the properties in the game (no groups). Display tables of coefficients and summaries for your model. 

```{r allpricemodel}

```

C) Fit a linear model that predicts property price as a function of spaces from Go for the street properties only. Display tables of coefficients and summaries for your model. 

```{r streetpricemodel}

```

D) Discuss the differences between the your models (e.g., equations, R^2^ values, residuals, other relevant measures of fit). Why did taking out the railroads and utilities produce these changes?

**ANSWER:**


### Session Info

**Names of Collaborators**:

```{r}
sessionInfo()
```